---
title: "EquationDrug Attribution"
author: "Benjamin J. Radford"
date: "March 12, 2015"
output: html_document
---

First, we'll use the `workalendar` module from Python to create a set of work-day distributions for various candidate countries.
```{r, engine='python', highlight=T}
# This code is in Python 2.7
# It uses the workalendar package to get natianal holidays for various countries.
from datetime import date
import csv
import os
from workalendar.europe import France, UnitedKingdom, Germany
from workalendar.canada import Canada
from workalendar.usa import UnitedStates
from workalendar.oceania import Australia
from workalendar.america import Brazil
cal = {'France':France(), 'UnitedKingdom':UnitedKingdom(), 
       'Germany':Germany(), 'Canada':Canada(), 
       'UnitedStates':UnitedStates(), 'Australia':Australia(),
       'Brazil':Brazil()}
with open('temp_holidays.csv','w') as my_file:
  csv_file = csv.writer(my_file)
  csv_file.writerow(['date','name','country'])
  for yy in range(2001,2013):
    for cc in cal:
      for dd in cal[cc].holidays(yy):
        dd = dd + (cc,)
        csv_file.writerow(dd)
```

Now we'll open our new holiday file in R as a dataframe. Then, we'll load the Equation Group's link timestamp dates into the R object `eq.dates`. These come from [Kaspersky Labs](http://securelist.com/blog/research/69203/inside-the-equationdrug-espionage-platform/). 
```{r, echo=T, error=F, message=F, warning=F, results='hide'}
# This code is in R.
# First, we read in the csv file we just created with holidays by country.
library(timeDate)
holiday <- read.csv("temp_holidays.csv", stringsAsFactors=F)
holiday$date <- as.Date(holiday$date)
holiday.list <- split(holiday, holiday$country)
file.remove("temp_holidays.csv")

eq.dates <- c("2001.08.17", "2007.12.11", "2009.04.16", "2011.10.20", "2012.08.31", "2013.06.11",
              "2001.08.23", "2007.12.17", "2009.06.05", "2011.10.26", "2012.09.28", "2013.06.26",
              "2003.08.16", "2008.01.01", "2009.12.15", "2012.03.06", "2012.10.23", "2013.08.09",
              "2003.08.17", "2008.01.23", "2010.01.22", "2012.03.22", "2012.11.02", "2013.08.28",
              "2005.03.16", "2008.01.24", "2010.02.19", "2012.04.03", "2012.11.06", "2013.10.16",
              "2005.09.08", "2008.01.29", "2010.02.22", "2012.04.04", "2013.01.08", "2013.11.04",
              "2006.06.15", "2008.01.30", "2010.03.27", "2012.04.05", "2013.02.07", "2013.11.26",
              "2006.09.18", "2008.04.24", "2010.06.15", "2012.04.12", "2013.02.21", "2013.12.04",
              "2006.10.04", "2008.05.07", "2011.02.09", "2012.07.02", "2013.02.22", "2013.12.05",
              "2006.10.16", "2008.05.09", "2011.02.23", "2012.07.09", "2013.02.27", "2013.12.13",
              "2007.07.12", "2008.06.17", "2011.08.08", "2012.07.17", "2013.04.16",
              "2007.10.02", "2008.09.17", "2011.08.30", "2012.08.02", "2013.05.08",
              "2007.10.16", "2008.09.24", "2011.09.02", "2012.08.03", "2013.05.14",
              "2007.12.10", "2008.12.05", "2011.10.04", "2012.08.14", "2013.05.24")
eq.dates <- as.Date(eq.dates,"%Y.%m.%d")

# Set parameters
all.dates <- seq(min(eq.dates),max(eq.dates),by=1)
all.dates <- all.dates[isWeekday(all.dates)]
sample.size <- length(eq.dates)
n <- 10000

# Simulate n link dates
sample.dates <- list()
for(ii in 1:n)
  sample.dates <- c(sample.dates, list(sample(all.dates, sample.size)))

# Calculate holiday distribution for each country
simulated.list <- list()
observed.list <- NULL
country.name <- NULL
for(cc in holiday.list)
{
  simulated.list <- c(simulated.list, list(lapply(sample.dates, FUN=function(x){sum(x %in% cc$date)})))
  observed.list <- c(observed.list, sum(eq.dates %in% cc$date))
  country.name <- c(country.name,unique(cc$country)) 
}
```

Finally, we will inspect the results.
```{r, warning=F, error=F, message=F, results='hold', comment=""}
results.df <- NULL
mfrow.val <- ceiling(sqrt(length(country.name)))
par(mfrow=c(mfrow.val,mfrow.val), mar=c(4.1,1.1,5.1,1.1))
for(cc in 1:length(country.name))
{
  c.name <- country.name[cc]
  proportion <- mean(simulated.list[[cc]] <= observed.list[cc])
  results.df <- rbind(results.df, data.frame(Country=c.name, Probability=proportion))
  hist(as.numeric(simulated.list[[cc]]), breaks=0:max(unlist(simulated.list)), col="#aaaaaa",
       ylab="", xlab="Links on Holidays", main=country.name[cc], yaxt="n", yaxs="i")
  abline(v=observed.list[cc], col="red", lwd=2)
}
print(results.df[order(results.df$Probability),], right=F, row.names=F)
```

This means that it is least likely for a set of dates with this few holidays to occur at random in the United States.
