---
title: "EquationDrug Attribution"
author: "Benjamin J. Radford"
date: "March 12, 2015"
output: html_document
---

```{r, engine='python', highlight=T, echo=F}
# This code is in Python 2.7
# It uses the workalendar package to get natianal holidays for various countries.
# from datetime import date
# import csv
# import os
# from workalendar.europe import France, UnitedKingdom, Germany
# from workalendar.canada import Canada
# from workalendar.usa import UnitedStates
# from workalendar.oceania import Australia
# from workalendar.america import Brazil
# cal = {'France':France(), 'UnitedKingdom':UnitedKingdom(), 
#        'Germany':Germany(), 'Canada':Canada(), 
#        'UnitedStates':UnitedStates(), 'Australia':Australia(),
#        'Brazil':Brazil()}
# with open('temp_holidays.csv','w') as my_file:
#   csv_file = csv.writer(my_file)
#   csv_file.writerow(['date','name','country'])
#   for yy in range(2001,2013):
#     for cc in cal:
#       for dd in cal[cc].holidays(yy):
#         dd = dd + (cc,)
#         csv_file.writerow(dd)
```

First, we will download the holidays for several candidate countries from [timeanddate.com](www.timeanddate.com). To do this, we'll use the [`XML`](http://cran.r-project.org/web/packages/XML/index.html) package in [`R`](http://www.r-project.org/).
```{r}
library(XML)
base.url <- "http://www.timeanddate.com/holidays"
countries <- c("russia","israel","china","iran","canada","uk","us","brazil","australia","new-zealand","germany")
years <- 2001:2013
holiday.list <- list()
for(yy in years)
{
  for(cc in countries)
  {
    cat("\r",cc," ",yy,"           ")
    holiday.url <- paste(base.url,cc,yy,sep="/")
    page <- htmlParse(holiday.url)
    tabs <- readHTMLTable(page, header=T)
    holiday.table <- tabs[[1]]
    holiday.table <- holiday.table[grepl("National holiday|Bank holiday|Public Holiday|Feriado Nacional",holiday.table[,4],ignore.case=T),]
    date <- paste(holiday.table[,1],yy,sep=" ")
    date <- as.Date(date, "%b %d %Y")
    name <- holiday.table[,3]
    holiday.list <- c(holiday.list,list(data.frame("date"=date,"name"=name,"country"=cc)))
    Sys.sleep(0.25)
  }
}
holiday.df <- do.call(rbind,holiday.list)
```

Now we'll open our new holiday file in R as a dataframe. Then, we'll load the Equation Group's link timestamp dates into the R object `eq.dates`. These come from [Kaspersky Labs](http://securelist.com/blog/research/69203/inside-the-equationdrug-espionage-platform/). 
```{r, echo=T, error=F, message=F, warning=F, results='hide'}
library(timeDate)
holiday.list <- split(holiday.df, holiday.df$country)

eq.dates <- c("2001.08.17", "2007.12.11", "2009.04.16", "2011.10.20", "2012.08.31", "2013.06.11",
              "2001.08.23", "2007.12.17", "2009.06.05", "2011.10.26", "2012.09.28", "2013.06.26",
              "2003.08.16", "2008.01.01", "2009.12.15", "2012.03.06", "2012.10.23", "2013.08.09",
              "2003.08.17", "2008.01.23", "2010.01.22", "2012.03.22", "2012.11.02", "2013.08.28",
              "2005.03.16", "2008.01.24", "2010.02.19", "2012.04.03", "2012.11.06", "2013.10.16",
              "2005.09.08", "2008.01.29", "2010.02.22", "2012.04.04", "2013.01.08", "2013.11.04",
              "2006.06.15", "2008.01.30", "2010.03.27", "2012.04.05", "2013.02.07", "2013.11.26",
              "2006.09.18", "2008.04.24", "2010.06.15", "2012.04.12", "2013.02.21", "2013.12.04",
              "2006.10.04", "2008.05.07", "2011.02.09", "2012.07.02", "2013.02.22", "2013.12.05",
              "2006.10.16", "2008.05.09", "2011.02.23", "2012.07.09", "2013.02.27", "2013.12.13",
              "2007.07.12", "2008.06.17", "2011.08.08", "2012.07.17", "2013.04.16",
              "2007.10.02", "2008.09.17", "2011.08.30", "2012.08.02", "2013.05.08",
              "2007.10.16", "2008.09.24", "2011.09.02", "2012.08.03", "2013.05.14",
              "2007.12.10", "2008.12.05", "2011.10.04", "2012.08.14", "2013.05.24")
eq.dates <- as.Date(eq.dates,"%Y.%m.%d")

# Set parameters
week.distribution <- table(dayOfWeek(timeDate(eq.dates)))
all.dates <- seq(min(eq.dates),max(eq.dates),by=1)
mon <- all.dates[dayOfWeek(timeDate(all.dates))=="Mon"]
tue <- all.dates[dayOfWeek(timeDate(all.dates))=="TUe"]
wed <- all.dates[dayOfWeek(timeDate(all.dates))=="Wed"]
thu <- all.dates[dayOfWeek(timeDate(all.dates))=="Thu"]
fri <- all.dates[dayOfWeek(timeDate(all.dates))=="Fri"]
sat <- all.dates[dayOfWeek(timeDate(all.dates))=="Sat"]
sun <- all.dates[dayOfWeek(timeDate(all.dates))=="Sun"]
n <- 10000

# Simulate n link dates
sample.dates <- list()
for(ii in 1:n)
{
  sample.mon <- sample(mon, week.distribution["Mon"], replace=F)
  sample.tue <- sample(mon, week.distribution["Tue"], replace=F)
  sample.wed <- sample(mon, week.distribution["Wed"], replace=F)
  sample.thu <- sample(mon, week.distribution["Thu"], replace=F)
  sample.fri <- sample(mon, week.distribution["Fri"], replace=F)
  sample.sat <- sample(mon, week.distribution["Sat"], replace=F)
  sample.sun <- sample(mon, week.distribution["Sun"], replace=F)
  week.sample <- c(sample.mon,sample.tue,sample.wed,sample.thu,sample.fri,sample.sat,sample.sun)
  sample.dates <- c(sample.dates, list(week.sample))
}

# Calculate holiday distribution for each country
simulated.list <- list()
observed.list <- NULL
country.name <- NULL
for(cc in holiday.list)
{
  simulated.list <- c(simulated.list, list(lapply(sample.dates, FUN=function(x){sum(x %in% cc$date)})))
  observed.list <- c(observed.list, sum(eq.dates %in% cc$date))
  country.name <- c(country.name,as.character(unique(cc$country)))
}
```

Finally, we will inspect the results.
```{r, warning=F, error=F, message=F, results='hold', comment=""}
results.df <- NULL

par(mfrow=c(4,3), mar=c(2.1,1.1,5.1,1.1))
for(cc in 1:length(country.name))
{
  c.name <- country.name[cc]
  proportion <- mean(simulated.list[[cc]] <= observed.list[cc])
  results.df <- rbind(results.df, data.frame(Country=c.name, Probability=proportion))
  hist(as.numeric(simulated.list[[cc]]), breaks=0:max(unlist(simulated.list)), col="#aaaaaa",
       ylab="", xlab="", main=toupper(country.name[cc]), yaxt="n", yaxs="i")
  abline(v=mean(as.numeric(simulated.list[[cc]])), col="blue", lwd=2)
  abline(v=observed.list[cc], col="red", lwd=2)
}
plot(0,0,type="n",xaxt="n",yaxt="n",main="",xlab="",ylab="",xlim=c(-1,1),ylim=c(0,3),frame=F)
text(0,.5,"Expected Value",col="blue")
text(0,2.5,"Observed Value",col="red")

print(results.df[order(results.df$Probability),], right=F, row.names=F)
```

This means that it is least likely for a set of dates with this few holidays to occur at random in the United States.
